### 2016-12-01 Projects/DelCo_2012/Report/DelCo_2012.tex
Added windows to floor plans

\begin{figure}[!ht]
	\includegraphics[width=.35\columnwidth]{../Figures/Floor_Plans/PDFs/DelCo_2012_Door_Legend}
	\caption{Door Status Legend}
	\label{fig:Door_Status_Legend}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Furniture}
	\caption{Furniture Fuel Load Dimensions in Single-Story Structure}
	\label{fig:Furniture_Fuel_Load_Dimensions}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Pallets}
	\caption{Wood Fuel Load Dimensions in Single-Story Structure}
	\label{fig:Wood_Fuel_Load_Dimensions}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Plain}
	\caption{Fully Dimensioned Floor Plan of the First Floor of the Two-Story Structure}
	\label{fig:dimensioned_first_2story_detailed}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_2nd_Floor_Plain}
	\caption{Fully Dimensioned Floor Plan of the Second Floor of the Two-Story Structure}
	\label{fig:dimensioned_second_2story_detailed}
\end{figure}

>>>>

\begin{figure}[!ht]
	\includegraphics[width=.35\columnwidth]{../Figures/Floor_Plans/PDFs/DelCo_2012_Door_Legend}
	\caption{Door and Window Legend}
	\label{fig:Door_Status_Legend}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Furniture}
	\caption{Furniture Fuel Load Dimensions in Single-Story Structure}
	\label{fig:Furniture_Fuel_Load_Dimensions}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Pallets}
	\caption{Wood Fuel Load Dimensions in Single-Story Structure}
	\label{fig:Wood_Fuel_Load_Dimensions}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Detailed}
	\caption{Fully Dimensioned Floor Plan of the First Floor of the Two-Story Structure}
	\label{fig:dimensioned_first_2story_detailed}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_2nd_Floor_Detailed}
	\caption{Fully Dimensioned Floor Plan of the Second Floor of the Two-Story Structure}
	\label{fig:dimensioned_second_2story_detailed}
\end{figure}
